---
title: "Lab3A"
author: "Raghid Alhazmy"
date: "9/7/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```

```{r eval=FALSE} 
 download.file(url="https://ndownloader.figshare.com/files/2292169",
              destfile = "data/portal_data_joined.csv")
```

eval=FALSE does not run the r block when kniting

```{r}
surveys <- read_csv("data/portal_data_joined.csv")
```

```{r}
head(surveys)
```

shows the first 6 rows

```{r eval=FALSE}
view(surveys)
```

```{r}
str(surveys)
```

```{r}
dim(surveys)
```

```{r}
summary(surveys)
```

### Challenge 1:
What is the class of the object surveys?
*tibble*

How many rows and how many columns are in this object?
*34786 rows and 13 columns*

How many species have been recorded during these surveys?
*48*
<br />
<br />
<br />
<br />
<br />

```{r}
# first element in the first column of the data frame (as a vector)
surveys[1, 1]   
# first element in the 6th column (as a vector)
surveys[1, 6]   
# first column of the data frame (as a vector)
surveys[, 1]    
# first column of the data frame (as a data.frame)
surveys[1]      
# first three elements in the 7th column (as a vector)
surveys[1:3, 7] 
# the 3rd row of the data frame (as a data.frame)
surveys[3, ]    
# equivalent to head_surveys <- head(surveys)
head_surveys <- surveys[1:6, ] 
surveys[, -1]         
# The whole data frame, except the first column
surveys[-(7:34786), ] 
# Equivalent to head(surveys)
```

```{r eval=FALSE}
surveys["species_id"]       # Result is a data.frame
surveys[, "species_id"]     # Result is a vector
surveys[["species_id"]]     # Result is a vector
surveys$species_id          # Result is a vector
```

### Challenge 2:
```{r}
surveyes_200 <- surveys[200, ]
n_rows <- nrow(surveys)
last <- surveys[n_rows, ]
middle <- surveys[n_rows / 2, ]
head <- surveys[-(7:n_rows), ]
head
```

```{r}
sex <- factor(c("male", "female", "female", "male"))
levels(sex)
nlevels(sex)
```

```{r}
sex <- factor(sex, levels = c("male", "female"))
levels(sex)
```


```{r}
year_fct <- factor(c(1990, 1983, 1977, 1998, 1990))
as.numeric(year_fct)
as.numeric(as.character(year_fct))
as.numeric(levels(year_fct))[year_fct]
```
We obtain all the factor levels using levels(year_fct)
We convert these levels to numeric values using as.numeric(levels(year_fct))
We then access these numeric values using the underlying integers of the vector year_fct inside the square brackets


```{r}
plot(as.factor(surveys$sex))
```

```{r}
sex <- factor(surveys$sex)
head(sex)
levels(sex)[3] <- "undetermined"
levels(sex)
head(sex)
```

### Challenge 3:
```{r}
levels(sex)[2:3] <- c("female", "male")
sex <- factor(sex, levels = c("female", "male", "undetermined"))
plot(sex)
```

```{r}
surveys <- read.csv("data/portal_data_joined.csv", stringsAsFactors = TRUE)
str(surveys)
surveys <- read.csv("data/portal_data_joined.csv", stringsAsFactors = FALSE)
str(surveys)
```


### Challenge 4:
```{r}
animal_data <- data.frame(
          animal = c("dog", "cat", "sea cucumber", "sea urchin"),
          feel = c("furry", "furry", "squishy", "spiny"),
          weight = c(45, 8, 1.1, 0.8)
          )

country_climate <- data.frame(
       country = c("Canada", "Panama", "South Africa", "Australia"),
       climate = c("cold", "hot", "temperate", "hot/temperate"),
       temperature = c(10, 30, 18, 15),
       northern_hemisphere = c(TRUE, TRUE, FALSE, FALSE),
       has_kangaroo = c(FALSE, FALSE, FALSE, TRUE)
       )
```

```{r}
library("lubridate")

my_date <- ymd("2015-01-01")
str(my_date)

my_date <- ymd(paste("2015", "1", "1", sep = "-")) 
str(my_date)
```

```{r eval=FALSE}
paste(surveys$year, surveys$month, surveys$day, sep = "-")
ymd(paste(surveys$year, surveys$month, surveys$day, sep = "-"))
```


