---
title: "Lab9"
author: "Raghid Alhazmy"
date: "11/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stringr)
library(tidyverse)
```

```{r}
x <- c("wheel", "feel", "water")
str_view(x, "ee")
```
```{r}
str_view(x, ".e.")
```
```{r}
# To create the regular expression, we need \\
dot <- "\\."

# But the expression itself only contains one:
writeLines(dot)
```
```{r}
# And this tells R to look for an explicit .
x <- c("abc", "a.c", "bef")
str_view(x, "a\\.c")
```
```{r}
x <- "a\\b"
writeLines(x)
```
```{r}
str_view(x, "\\\\")
```
## 14.3.1.1 Exercises
####1. 4 \\\\ are required to use '\' as an escape character. the first two \\ are used to create a regulare expression, and another \ to make it a string.
####2. x <- ""'\"  str_view(x, "\"'\\\\")
####3. x<-"1.2.3.4.5"    str_view(x, "\..\..\..")     .2.3.4

```{r}
x <- c("apple", "banana", "pear")
str_view(x, "^a")
```
```{r}
str_view(x, "a$")
```

```{r}
x <- c("apple pie", "apple", "apple cake")
str_view(x, "^apple$")
```

##14.3.2.1 Exercises

```{r}
#1.
x <- c("$^$")
str_view(x, "\\$\\^\\$")
```

```{r, eval=FALSE}
#2.
str_view(stringr::words, "^y")
str_view(stringr::words, "x$")
str_view(stringr::words, "^...$")
str_view(stringr::words, ".......")
```

```{r}
x <- c("abc", "a.c", "a*c", "a c")
str_view(x, "a[.]c")
```
```{r}
str_view(x, ".[*]c")
```
```{r}
str_view(x, "a[ ]")
```
```{r}
x <- c("grey", "gray")
str_view(x, "gr(e|a)y")
```
##14.3.3.1 Exercises
```{r, eval=FALSE}
#1.
w<-stringr::words
str_view(w, "^[aeiou]")
str_view(w, "[aeiou]", match = FALSE)
str_view(w, "[^e]ed$")
str_view(w, "ing$|ise$")
```
```{r, eval=FALSE}
#2.
str_view(w, "ie|[^c]ei")
```
```{r, eval=FALSE}
#3.
str_view(w, "q[^u]")
```
```{r, eval=FALSE}
#4.
str_view(w, "ou")
```

```{r}
x <- "1888 is the longest year in Roman numerals: MDCCCLXXXVIII"
str_view(x, "CC?")
```
```{r}
str_view(x, "CC+")
```
```{r}
str_view(x, 'C[LX]+')
```

{n}: exactly n
{n,}: n or more
{,m}: at most m
{n,m}: between n and m

##14.3.4.1 Exercises
####1. ? = {0,1}  + = {1,}  * = {0,}
####2. ^.*$ will match with anything    \\{.+\\} will match with anything inside{}    \d{4}-\d{2}-\d{2} will match with ####-##-##    \\\\{4} will match with 8 \ ex. \\\\\\\\
```{r, eval=FALSE}
#3.
str_view(w, "^[aeiou]{3}")
str_view(w, "[aeiou]{3,}")
str_view(w, "([aeiou][^aeiou]){2,}")
```

##14.3.5.1 Exercises
####1. (.)\1\1 macthes a repeating character    (.)(.)\\2\\1 matches a pair of characters foloowed by the reverse of those characters   (..)\1 matches with a repeating pair of characters    (.).\\1.\\1 matches with ex. abaca repeating the original character and any character in between.   (.)(.)(.).*\\3\\2\\1  matches with three characters, then any number of charcters, then the original three characters in reverse order.
```{r, eval=FALSE}
#2.
str_view(w, "(.).*\1")
str_view(w, "(.)(.).*\1\2")
str_view(w, "(.).*\1.*\1.*")
```

```{r}
x <- c("apple", "banana", "pear")
str_detect(x, "e")
```
```{r}
# How many common words start with t?
sum(str_detect(words, "^t"))
```
```{r}
# What proportion of common words end with a vowel?
mean(str_detect(words, "[aeiou]$"))
```
```{r}
# Find all words containing at least one vowel, and negate
no_vowels_1 <- !str_detect(words, "[aeiou]")
# Find all words consisting only of consonants (non-vowels)
no_vowels_2 <- str_detect(words, "^[^aeiou]+$")
identical(no_vowels_1, no_vowels_2)
```
```{r}
words[str_detect(words, "x$")]
str_subset(words, "x$")
```
```{r}
x <- c("apple", "banana", "pear")
str_count(x, "a")
```

```{r}
# On average, how many vowels per word?
mean(str_count(words, "[aeiou]"))
```

##14.4.1.1 Exercises
```{r}
#1.
words[str_detect(words, "^x|x$")]

xstart <- str_detect(words, "^x")
xlast <- str_detect(words, "x$")
words[xstart | xlast]
```
```{r}
#2.
str_subset(words, "^[aeiou].*[^aeiou]$")

vowelstart <- str_detect(words, "^[aeiou]")
con_end <- str_detect(words, "[^aeiou]$")
words[vowelstart & con_end]
```

```{r}
colours <- c("red", "orange", "yellow", "green", "blue", "purple")
colour_match <- str_c(colours, collapse = "|")
colour_match

has_colour <- str_subset(sentences, colour_match)
matches <- str_extract(has_colour, colour_match)
head(matches)
```

```{r}
more <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more, colour_match)
```

##14.4.2.1 Exercises
```{r}
#1.
colour_match2 <- str_c("\\b(", str_c(colours, collapse = "|"), ")\\b")
colour_match2

more2 <- sentences[str_count(sentences, colour_match) > 1]
str_view_all(more2, colour_match2)
```
```{r}
#2.
str_extract(sentences, "[A-ZAa-z]+") %>% head()

pattern <- "\\b[A-Za-z]+ing\\b"
sentences_with_ing <- str_detect(sentences, pattern)
unique(unlist(str_extract_all(sentences[sentences_with_ing], pattern)))

unique(unlist(str_extract_all(sentences, "\\b[A-Za-z]{3,}s\\b")))
```

```{r}
noun <- "(a|the) ([^ ]+)"

has_noun <- sentences %>%
  str_subset(noun) %>%
  head(10)
has_noun %>% 
  str_extract(noun)
```
```{r}
has_noun %>% 
  str_match(noun)
```

```{r}
tibble(sentence = sentences) %>% 
  tidyr::extract(
    sentence, c("article", "noun"), "(a|the) ([^ ]+)", 
    remove = FALSE
  )
```

##14.4.3.1 Exercises
```{r}
#1.
numbers <- "\\b(one|two|three|four|five|six|seven|eight|nine|ten) +(\\w+)"
sentences[str_detect(sentences, numbers)] %>%
  str_extract(numbers)
```
```{r}
#2.
contraction <- "([A-Za-z]+)'([A-Za-z]+)"
sentences[str_detect(sentences, contraction)] %>%
  str_extract(contraction) %>%
  str_split("'")
```

```{r}
x <- c("apple", "pear", "banana")
str_replace(x, "[aeiou]", "-")
str_replace_all(x, "[aeiou]", "-")
```

```{r}
x <- c("1 house", "2 cars", "3 people")
str_replace_all(x, c("1" = "one", "2" = "two", "3" = "three"))
```

##14.4.4.1 Exercises
```{r}
#1.
str_replace_all("one/two/three/four", "/", "\\\\")
```
```{r}
#2.
replacements <- c("A" = "a", "B" = "b", "C" = "c", "D" = "d", "E" = "e",
                  "F" = "f", "G" = "g", "H" = "h", "I" = "i", "J" = "j", 
                  "K" = "k", "L" = "l", "M" = "m", "N" = "n", "O" = "o", 
                  "P" = "p", "Q" = "q", "R" = "r", "S" = "s", "T" = "t", 
                  "U" = "u", "V" = "v", "W" = "w", "X" = "x", "Y" = "y", 
                  "Z" = "z")
lower_words <- str_replace_all(words, pattern = replacements)
```
```{r}
#3.
str_replace_all(words, "^([A-Za-z])(.*)([A-Za-z])$", "\\3\\2\\1")
```

```{r}
sentences %>%
  head(5) %>% 
  str_split(" ")
```
```{r}
"a|b|c|d" %>% 
  str_split("\\|") %>% 
  .[[1]]
```
```{r}
sentences %>%
  head(5) %>% 
  str_split(" ", simplify = TRUE)
```
```{r}
fields <- c("Name: Hadley", "Country: NZ", "Age: 35")
fields %>% str_split(": ", n = 2, simplify = TRUE)
```
```{r}
x <- "This is a sentence.  This is another sentence."
str_view_all(x, boundary("word"))
```
```{r}
str_split(x, " ")[[1]]
```
```{r}
str_split(x, boundary("word"))[[1]]
```

##14.4.5.1 Exercises
```{r}
x <- c("apples, pears, and bananas")
str_split(x, ", +(and +)?")[[1]]
```

